\vspace{-1em}Guidance, please! Towards a framework for RDF-based constraint languages.

### 2015-07-17 paper/paper 2/dc-2015.tex
introduction

With its direct support of validation via SPARQL, the \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org/}} is also very popular to formulate and check constraints \cite{Fuerber2010}. We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although SPARQL aficionados might object particularly to the latter point.

@@

We formerly demonstrated that a high-level constraint language, Description Set Profiles, can be implemented by mapping the language to SPIN using SPARQL CONSTRUCT queries \cite{BoschEckert2014-2}. We provide a validation environment where own mappings from arbitrary constraint languages can be provided and tested.\footnote{Available at \url{http://purl.org/net/rdfval-demo}, source code available at: \url{https://github.com/boschthomas/rdf-validator}.}

The creation of such mappings is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates:

The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES. Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be used to formulate the constraint
that \emph{publications} must have at least one \emph{author} which must be a \emph{person}.

This constraint can be expressed as follows using different constraint languages:

@@

Note that the SPIN representation is NOT a mapping, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated. The mapping for DSP is much more complicated and can be found in the mappings provided by us.\footnote{Online: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}

>>>>

With its direct support of validation via SPARQL, the \emph{SPARQL Inferencing Notation (SPIN)}\footnote{\url{http://spinrdf.org/}} is also very popular to formulate and check constraints \cite{Fuerber2010}. We consider SPIN as a low-level language in contrast to the other constraint languages where specific language constructs exist to define constraints in a declarative and in comparison more intuitive way -- although, SPARQL aficionados might object particularly to the latter point.

@@

We formerly demonstrated that a high-level constraint language like OWL 2 and DSP can be implemented by mapping the language to SPIN using SPARQL CONSTRUCT queries \cite{BoschEckert2014-2}. We provide a validation environment where own mappings from arbitrary constraint languages can be provided and tested\footnote{Online available at: \url{http://purl.org/net/rdfval-demo}, source code online available at: \url{https://github.com/boschthomas/rdf-validator}.}. The only limitations are that the constraints have to
be expressed in RDF and that the constraint language is expressable in SPARQL.

The creation of such mappings is in many cases not straight-forward and requires profound knowledge of SPARQL, as the following example demonstrates. 
The constraint type \emph{minimum qualified cardinality restrictions} which corresponds to the requirement \emph{R-75}\footnote{Requirements are identified in the database by an R and a number, additionally an alphanumeric identifier is provided, in this case R-75-MINIMUM-QUALIFIED-CARDINALITY-ON-PROPERTIES. Online at: \url{http://lelystad.informatik.uni-mannheim.de/rdf-validation/?q=node/82}} can be used to formulate the constraint that publications must have at least one author which must be a person. This constraint can be expressed as follows using different constraint languages:

@@

Note that the SPIN representation is NOT a mapping, but a direct expression of the constraint using a SPARQL CONSTRUCT query that creates a spin:ConstraintViolation if the constraint is violated. The mapping for DSP is much more complicated and can be found in the mappings provided by us\footnote{Online available at: \url{https://github.com/boschthomas/rdf-validation/blob/b6a275fb5d71a92ae33d3b6aadd5f447351214b7/SPIN/DSP_SPIN-Mapping.ttl#L4665}}.
